Finding GENERAL Defect Prediction Models Within Hundreds of Software Projects

### 2020-03-19 response.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               RESPONSE TO REVIEWERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak
\newpage
\renewcommand*{\thesection}{\Alph{section}}
\nobalance
\section*{RESPONSE TO REVIEWERS}
\section*{Comments from the editor}

\review{I would like to thank the authors for submitting their work to TSE. While all the reviewers agree that the problem addressed is important and the paper has potential, the reviewers also identified several concerns that need to be carefully addressed. The reviewers also agreed that the amount of work needed to address those concerns is beyond a major revision. Thus, after carefully checking the reviewers and in accordance with reviewer’s recommendations, I also recommend “Revise and resubmit as New”.}

\response{ Thank you very much for your encouraging comments. We find that the prior draft made
several mistakes, that have been fixed here.
\bi
\item We assumed that the  core motivation for this work
was widely known and accepted in the community. That was a mistake. This draft completely rewrites the Introduction
to include much more background information on the 
presence of the problem studied here.
\item Cascading on from that first mistake, we made several
mistakes with how we framed   our research questions. This
draft fixes those errors. This has the added benefit
of clarifying our discussion
along the way.
\ei
Apart from these two points we have also addressed
the many helpful and detailed comments from the reviewers:
\be
\item The problem statement has been  clarified and properly positioned (R1, R3).
\item The novelty of the approach has  been clarified (R3). (see \bareresp{3-1})
\item Using comments from  (R1, R2, R3), we have made numerous small editorial improvements.
\item The study now includes all the details to ensure 
replicability   (R1, R2).
\item The results of the study need to be revisited since the reviewers are not convinced that the results support the claims in the paper (R1, R2, R3).
\item The background on transfer learning has been augmented with more  citations (R2).
\ee
}

@@

\section*{Reviewer 1}

\response{Thank you very much for your detailed review.
As we said to the associated editor, the previous draft made the following mistake:
\bi
\item We assumed that the  core motivation for this work
was widely known and accepted in the community. That was a mistake. 
\item
Consequently,this draft completely rewrites the Introduction
to include much more background information on the 
presence of the problem studied here.
\ei
We have made some additional corrections, clarifications, and revisions, as directed by your comments. To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.}

@@

\review{(1.1a) Background. The paper builds upon a number of previous studies. However, several key questions have no answer: *What is* the bellwether? *Why is* this relevant? How does it work when applied to different contexts? Why is this useful in practice?}

\response{(1.1b)You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1\citeresp{1-1a}}

\begin{quote}
    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others. (the bellwether is the  leading sheep of a flock, with a bell on its neck)}
\end{quote}

@@

\review{The paper mentions that: "The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects": very good, but where this intuition come from?}

\response{Thank you for that comment.  You are quite correct-- we did not document the source of our intuition. We have added the following note to \citeresp{1-1b}}

\begin{quote}
\response{``The core intuition of this new approach is two-fold. Firstly,
many projects are similar in structure. We came to this
intuition based on the writing
of    Devanbu
et al.`\cite{hindle2012naturalness}   who showed that a remarkably
small number of Markov chains 
capture the repeated patterns
of tokens in a program~\\
When such similarities
exist, then we   exploit symmetries between different projects in order to learn predictors from one and apply those to another. Specifically: assuming inter-project symmetry,   we do not need to run comparisons between all pairs of projects since analyzing just a few pairs should work as well as anything else.''}
\end{quote}

@@

\review{(1.2)The relevance of the paper. This is, unfortunately, unclear. According to the abstract and introduction, the main issue treated in the paper is related to scalability. Please, provide a clear case study on the performance of bellwether methods. The claims on the scalability of the approaches are just claims, no details are reported. Abstract and introduction just report that "when applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwether". As said, the bellwether approach has been applied to several problems (e.g., defect prediction/effort estimation/bad smell detection): are these problems the same? When is it needed to apply scalable solutions for bellwether approaches? Why? Please, explain.}

\response{Thank you for your comments.
 On review, we found that core problem of conclusion instability
was not well documented in the introduction. This new draft fixes that problem with a completely new
introduction that better focuses the work on conclusion instability and scalability.}

% {need a new RQ0: how slow is standard bellwether. theoretically an empirically its slow (chart on p2. move to RQ0). May need to include results using increasing community size.XXX including an comparison study with varying size of community to start with. Still need to write this}

@@

\review{(1.3a) Writing style. The introduction is, simply, to be completely rewritten}

\response{Thank you for your comment. We agree.   Much of the new
text on page1 takes care to document {\em why }
we are exploring conclusion instability before
moving on the {\em how} we do that exploration.}

\review{(1.3a)I would like to see a paper that is understandable even from non-experts. As such, please define the context of the paper, the concepts of (1) software quality - line 1, (2) general models - line 2, (3) many projects - line 2, (4) "scalable approach to learning effective models adapted to the task at hand" - line 2/3, (5) "or does the truth lie somewhere in-between" - line 3. These are just of the examples of why the introduction is unclear and does not provide any detail on the reasons behind the paper. The same is true for the remaining of the paper, which gives for granted many of the concepts without explaining them properly.}

\response{Thank you for your comment. We have deleted much of that confusing terminology from the introduction since, as you say, it introduces too many ideas in a confusing way, all at once.  Please see \citeresp{1-3}.}

@@

\review{(1.4) Please, avoid claims such as "have tremendous practical significance" without providing any practical significant example/citation. (This is just an example)}

\response{ Thank you for your comment, You are right.In this manuscript we have deleted the  superlatives (including that one)}

@@

\review{(1.5a) The clarity and replicability of the paper are unclear. Here some examples 1) "The logistic regression learner (since it is relatively fast)". What does "fast" mean? How was "fast" computed? }

\response{ Thank you for your comment, you are quite right. We had not properly mentioned the reason behind choosing logistics regression.  In this draft we have added the reasons to \citeresp{1-5a}:}

\begin{quote}
\response{
"The logistic regression learner,  since it is widely used in defect prediction~\cite{ghotra2015revisiting} in   the  software engineering domain and, in our experience,
in runs much faster (in terms of model building time) than many other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc. (when tested on defect prediction).}
\end{quote}

\review{(1.5b) "The SMOTE class imbalance correction algorithm [49], which we run on the training data2". Why is SMOTE needed? Why is the problem unbalanced? Please, explain.
}

\response{You are right, we had not included the reason for using SMOTE in our algorithm and had not explained why the problem is unbalanced. In this draft we have added notes to answer those questions \citeresp{1-5b}:}
\begin{quote}
    \response{The SMOTE class imbalance correction algorithm~\cite{Chawla2002}, since many of the projects have relatively very few or large number of defects. A model build on project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have low recall or high recall with high pf). Thus we run SMOTE on the training data to artificially boost the number of target examples in the training data and achieving balanced recall and pf for the minority class test examples}
\end{quote}

\review{(1.5c) "and Hall’s CFS feature selector". Which features have been removed and why?
}

\response{You are quite correct, we did not included the details about how the features are being removed and why in the last draft. In this draft we have included notes regarding how CFS works and why the features that are not used are removed \citeresp{1-5b}:}

@@

\begin{quote}
    \response{Hall's CFS feature selector~\cite{hall1999correlation} is used to identify features which are highly correlated with the classification, yet uncorrelated to each other. The features which are  highly correlated with each other will not add more information while making classification, while the features which are uncorrelated towards the classification also not add more information while making classification. The CFS algorithm incrementally picks one feature at a time which adds the most information towards the classification at a given step and stops when there is no more improvement in the score.}
\end{quote}

\response{As to what attributes were selected, please see Figure~\ref{fig:FSS_compare}. As to what of
the selected figures were most important, please see Table~\ref{tbl:coefs}.}

\review{(1.5d) "As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most". Where can the reader understand this statement? Where is the replication data?}

\response{Thank you for your comment, using the replication package (including data) the experiments can be reproduced.\citeresp{1-5d}.  Also, we have added in specific numbers to that sentence:
\begin{quote}
As to CFS, we found that without it, our recalls were very low (less than 20\%).
\end{quote}
}

\review{(1.5e) "extensive studies have found that CFS more useful than many other feature subset selection methods such as PCA or InfoGain or RELIEF". The paper cites just one paper, how should these studies be "extensive"?}

\response{Thank you for that comment.  You are quite correct-- we did not document the all the necessary citations for supporting our claim before. We have added the following note to \citeresp{1-5e}}

\review{(1.5f) "Maximize recall and precision and popt(20)": Why should these metrics be maximized? What is the practical value, e.g., is high recall always needed in practice, or should we prefer precision in the problems treated by the bellwether? What about popt(20)?}

\response{Thank you for your comment, we didn't explained why these metrics need to be maximized, added necessary details\citeresp{1-5f}.}

@@

\review{(1.5g) "While minimizing false alarms and ifa auc": Again, please explain the practical relevance of the performance metrics employed. }

\response{Thank you for your comment, we didn't explained why these metrics need to be minimized, added necessary details\citeresp{1-5f}.}

@@

\review{(1.5h) 
More in general, how can one replicate the performed study? Is there a replication package? If so, where?}

\response{Thank you for that comment. You are quite correct-- we did not include in depth steps to replicate the study before. We have added a replication package in contribution section \citeresp{1-5h} as well as more in depth details about the algorithm has been added in figure~\ref{fig:Pseudo-code} and section~\ref{GENERAL}.}

@@

\review{(1.6a) The analysis of the results should be substantially improved. Let consider the case of Section 5 - RQ1. The results are reported in less than half column and refer to a figure (Figure 6) which does not explain anything. The summary reports that "Theoretically and empirically, the hierarchical reasoning on GENERAL performs much faster than standard bellwether methods": I cannot understand where these "theoretically and empirically" come from, since there is no proof of them. }

\response{You are quite correct. In the last draft we indeed did not included detailed analysis of the results to show the scalability of our model. In this draft \citeresp{1-2}\citeresp{1-6a} we have included 2 more research questions (RQ1 and RQ2) to show the conventional bellwether is slower than the new bellwether (aka GENERAL) method. We also have updated another research question (RQ3) to compare the methods in-term of number of comparisons and time taken to run the two methods, as can been seen in figure~\ref{fig:compare} and \ref{fig:compare_time}.}

@@

\review{(1.6b)
The same is true for the other research questions. And, in general, there is qualitative analysis: Why are the results the ones reported in the paper?}

\response{You are right,Thank you for that comments. We have added much  quantitative analysis as
well as statistical tests to this paper. Please see Figures~\ref{fig:compare_time} and ~\ref{fig:compare}.}

@@

\review{(1.6c) What makes the reported method scalable?}

\response{Thank you for your comment, in this version we have updated the RQ3 to show that our method is scalable. We have showcased the analysis of number of comparisons and run time between the two algorithm (conventional bellwether and GENERAL) using various community size.}

\section*{Reviewer 2}

\response{Thank you very much for your detailed review.
As we said to the associated editor, the previous draft made the following mistake:
\bi
\item We assumed that the  core motivation for this work
was widely known and accepted in the community. That was a mistake. 
\item
Consequently,this draft completely rewrites the Introduction
to include much more background information on the 
presence of the problem studied here.
\ei
We have made some additional corrections, clarifications, and revisions, as directed by your comments. To assist in your review, we refer to specific locations of each of the changes using the notation \respto{1-XX}.}

% Many of your comments take issue with two terms used in this paper "lessons learned" and "transfer learning".
% We agree with you that our use of "lessons learned" was inappropriate and we have removed all those usages.

% As to our use of "transfer learning", 
% inspired by your comments we have clarified what we mean by that term much earlier in the paper (see \cite{XXX}). Base don that clarification, we can show that our use of ``transfer learning'' is consistent with its usage by Pan'09 (a paper current 8,220 citations at the time of this writing)~\cite{pan2009survey}. Also, our usage is consistent with dozens of recent SE research papers on transfer learning~\cite{pan2009survey,kocaguneli2015transfer,jing2015heterogeneous,ma2012transfer,nam2013transfer,jamshidi2017transfer,qing2015cross,cao2015software,tong2016heterogeneous,nam2017heterogeneous,li2018cost,zhang2016cross,jing2015heterogeneous}. Thank you for encouraging us to clarify that terminology.

% A survey on transfer learning
% SJ Pan, Q Yang - IEEE Transactions on knowledge and data …, 2009 - ieeexplore.ieee.org
%   Cited by 8220 Related articles All 20 versions Web of Science: 3428

@@

% \review{These lessons learned are reviewed when new projects are being initiated/planned. The introduction talks about guiding project management but project management has a process for handling lessons learned that doesn’t require machine learning. How does the method help that process? Why would you need a “bellwether” to apply lessons learned to a new project?! The method does not transfer lessons learned but what it DOES appear to do is associate defect rate profiles for two projects (a so-called “bellwether” and a new project).}

% \response{ ur rught we renamed as you said. }

\review{(2.2) [Sec. 1] “…the bellwether is equivalent to the other models…” This claim is confusing. 1) Is “the bellwether” a model or a project? 2) How is equivalence defined? Or do you simply mean “similar”?}

\response{ Thank you for your comment, in the last draft we did not accurately explain what bellwether is. In this draft we have included the definition of bellwether \citeresp{1-1a}\citeresp{2-2}:}

\begin{quote}
    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others.} 
\end{quote}
\begin{quote}
    \response{Also, to answer your second question, ``…the bellwether is equivalent to the other models'' has been replaced with ``....since the bellwether is an exemplar projects for the community of N projects seen so far...''  }
\end{quote}

\review{(2.3) [Sec. 1] “when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).” }

\response{Thank you for your comment, this was a needless complexity that we deleted from this draft.}

@@

\review{(2.4) If the point is to use the bellwether to infer things about a “new” project, then how new can the new project be? When (in the new project’s history) can you be sure the model from the bellwether is valid to use?}

\response{Thank you for your comment. To answer the first question, the projects can be completely new projects, without any historical data collected for reference. To answer the second question, in this research the experiments has been designed to simulate a situation, where there are known projects in a large community as well as a set of new projects which are not part of the community. We do this by dividing the 697 projects into two sets 1) {\em Train 1}: a community 627 projects, from which we will select a bellwether and 2) {\em Train 2}: a set of 70 new projects, which will be tested using bellwether.}

% \response{Explain the train, test splits and the how you do the exp. then say this is what our model proves, it predicts for projects which it has not seen before XX.}

@@

\review{(2.5) Do you have to find a bellwether for each purpose? In other words, if you find a bellwether among 697 projects for defect rate prediction, then is that same bellwether automatically used to build a model for another discrete task (different than defect rate prediction)? Or will you have to apply this algorithm for each and every discrete task?}

\response{Thank you for your comment. 
As you point out, the prior draft
was too value on this point.
This paper now focuses on defect prediction (see the new title).}

\response{ But to answer
your question (about whether
or not the the bellwether changes
per goal), it is possible that another
task will require another bellwether.
Accordingly,
we assert it is vital that the
bellwether method is fast. Hence this paper.}

@@

\review{(2.6) Figure 1 needs to be omitted}

\response{You are correct. Deleted. }

\review{(2.7) The computational complexity $(O(N^2)$ versus $O(m*(N/m^2))$ is both compact appropriate.}

\response{In practice, the difference
between the runtimes associated with these two  approaches is a 
very large difference (as witnessed
by P  Figures~\ref{fig:compare_time} and ~\ref{fig:compare}.) }

@@

\review{(2.8) The paper does not evaluate the model’s performance using a pool of 12,000 projects; the evaluation does not even use 1,000 projects.}

\response{All our current numbers now say 697.}

\review{(2.9) [Sec. 1] The box under RQ4 is very confusing. We find the bellwether to simply study one project, but this note says we still need to analyze hundreds of projects to understand something like the importance of features. Is this right?}

\response{You are correct. We have reworded the wording of the box under RQ4, which was confusing. We have simpler text now \citeresp{2-9}.}

@@

% \response{(2.10e) 
% [C] There is no transfer learning done in Steps 4-6.}

% \response{(2.10f) 
% [D] Aside from inspecting each step in the main procedure, another way to determine whether GENERAL involves transfer learning is the following: This approach does not involve reweighting instances nor does it appear to involve transferring feature representations and/or parameters…and if it does then the paper does not even identify this fact much less argue for it being the case.
% If something in this rationale [A-D] is not correct, then please clear up the explanation on transfer learning in the paper in terms/language the machine learning community has established to avoid ambiguity.}

\review{(2.10) I do not understand what the second contribution really is.}

\response{
Thank you for that comment. We deleted it.}

%  \response{
% Note that with that new introduction (that focuses more on {\em why}, then this paper is not  better at contextualizing
% and justifying the need (and value) of the second contribution.}

@@

\review{(2.13) [Sec. 2.2] At least two-thirds of this sub-section is anecdotal. Does the gist of this subsection depend critically on the hypothetical?}

\response{Thank you for your comments. As you suggested, we have removed it.}

\review{(2.14) [Sec. 2.3] “Accordingly, here, we explore nearly 700 projects.” But just because 697 (this study) is larger than 24 (previous studies) does not mean external validity concerns are adequately addressed when one considers how complex the task is. Please comment.}

\response{Please see our new comments at end of introduction. Clearly, we oversold our case before. Our conclusions are not general to all projects. However, and this has not be achieved before. our conclusions are general to hundreds
of project.}

### 2020-03-19 manuscript.tex
Updates from Overleaf

\begin{document}
\title{  How to Find GENERAL    Defect Prediction Models  \\
Amidst Hundreds of    Software Projects}

@@

\IEEEtitleabstractindextext{%
\begin{abstract}
\respto{2-22}{\color{blue} When one   exemplar project, which we call the ``bellwether'', offers the best prediction
then
it can be used to offer prediction for
many other projects. Such bellwethers can be used to make quality predictions about new projects, even before there is much experience with those new projects.}
% Such general conclusions   simplifies     software quality policies since the list of quality problems, and their mitigations, is static). Also such general conclusions simplify the design and delivery
% of training programs since, as long as the bellwether offers best advice,
% then  ``best practices'' will remain  now constant.
% Lastly, bellwethers simplify tool development
% since, using the advice from the bellwether,  it is clear where it is most cost-effective to buy/build tools to mitigate
% for software quality issues.

But  existing  methods  for  bellwether  transfer  are  very slow.  When  applied  to  the  697  projects  studied  here,  they took  60  days  of  CPU  to  find  and  certify  the  bellwethers
Hence,  we  propose GENERAL:  a novel bellwether detection algorithm based on
  hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
This hierarchical method is a scalable approach to learning effective models from very
large data sets. 
For nearly 700 projects,
the defect prediction models generated from GENERAL's bellwether  
were  just as good as those found via  standard methods.

% Having shown that it is
% possible to transfer lessons learned across
%  100s of projects, our future work
%  will be to  achieve ``mega-transfer'';
%  i.e. to transfer lessons learned between
%  1000s to 10,000s of projects.

@@

\respto{1-3}{\color{blue}Researchers and industry practitioners makes use of data-driven decision making for defect prediction by generating software quality models(defect predictor) from project data comprises of software quality metrics (Commonly used software metrics for defect prediction are complexity metrics (such as lines of code, Halstead metrics, McCabe’s cyclometic complexity, and CK metrics) and process metrics (such as number of revisions, lines added and deleted) These defect predictors are used for predicting defects in new set of changes and to learn what are the important metrics that are responsible for finding these defects. These quality metrics can be collected with much ease from the code base of different software systems from large organizations and open source community, and can be used for large scale data-driven decision making.}

{\color{blue} But what is the external validity of the conclusions reached  via
the above data mining methods?
 If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.
 Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold.
Also, Kim et al.~\cite{Kim2016}, notes  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals. Many other researchers agree. For example,
Tan et al.~\cite{tan2016defining} say that such   insights  are a core deliverable. Sawyer et al. agree, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}. Also,
Bird, Zimmermann, et al.~\cite{Bird:2015} argue that such  insights occur when users reflect, and react, to the output of a model generated via software analytics. But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.}

{\color{blue} Apart from the above,  are several other reasons to seek general conclusions in SE. For example, 
if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
Also,
consider the task of training a   novice software engineers or newcomers to a project If our models are not stable, then it hard to teach what factors  most influence software quality.}

@@

{\color{blue} Finding general defect prediction models  across multiple projects is a complex task.
There are many recent examples of supposed ``general'' SE conclusions that are
now questionable. For example, Fenton warns
that, in stark contrast to  much prior research, pre- and post- release failures are not connected~\cite{fenton2000quantitative}.
Also, Nagappan et al. have found that the language construct GOTO, as used in contemporary practice, is rarely considered harmful~\cite{nagappan2015empirical};
Similiary, Fucci et al. report that test-driven development is not any better than "test last"~\cite{fucci2017dissection};
 Further, in our own work, we have seen that
 delayed issues are not exponentially more expensive to fix~\cite{menzies2017delayed}.
 For a long list of other conclusions that were found to be  unstable across multiple projects, see~\cite{Me13}. This problem is so endemic in software engineering that other journals have devoted entire special issues t the topic~\cite{Menzies2012}. }

{\color{blue} Given all these examples of SE conclusions whose generality we must now question, it is timely
to ask what methods are available for finding general results that hold across multiple projects?}
A new approach, that shows much promise, is the ``bellwether'' method for transferring conclusions between projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}. \respto{1-1a}{\color{blue} ``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others.} (the bellwether is the  leading sheep of a flock, with a bell on its neck).  This method:
\bi
\item Finds a  ``bellwether'' project that is exemplar for the rest;
\item Draw conclusions from  that project.
\ei
\respto{3-5}{\color{blue}This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization (In this paper we only explore defect prediction). As a method of transfer learning from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}}.

When new projects arrive, then even before there is much experience with those new projects,  models learned from other projects can be applied to the new project (just by studying the bellwether),
 Further, \respto{2-2}{\color{blue} since the bellwether is an exemplar projects for the community of N projects seen so far},
 %since the bellwether is similar to the other models
 then when new projects appear, \respto{2-3}{\color{blue} bugs can be localized for that project} even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
 %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
 %or (b)~best practices to avoid quality problems;
 %or (c)~cost-benefit justifications for buying or building tools can be made stable across a large number 
 %of projects.

But existing  methods for bellwether transfer are very slow. When applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwethers. There are many reasons for that including how the models were certified (20 repeats  with different train/test sets)
and the complexity of the analysis procedure (which includes fixing class imbalance and feature selection). But the major cause of this slow down was that those   methods  required an $O(N^2)$ comparison between   $N=697$ projects.

This paper reports a novel approach  that improves on existing bellwether methods.
%dramatically improves on existing bellwether methods.
 Our GENERAL  method  uses hierarchical clustering model to recursively divide a large number of projects into smaller clusters. Starting at the leaves of that tree of clusters, GENERAL finds the    bellwethers within sibling projects. That bellwether is then promoted up the tree. The output of GENERAL is the project promoted to the top of the tree of clusters.

 This paper evaluates the model built from the project   found by GENERAL. 
 We will find that  the predictions
 from this model  are as good, or better,
 than those found  via ``within'' learning (where models are trained and tested on local data)
 or ``all-pairs'' learning (where models are found after building models from all pairs of projects).
   That is
\begin{quote}
{\em 
Learning from many other projects can be better than learning just from your own local project data.
}\end{quote}
GENERAL's clustering methods divide $N$ projects into $m$ groups. In that space,   GENERAL only needs
to compare $O(m*(N/m)^2)$  projects to find the bellwether. Theoretically and empirically, 
this means GENERAL will scale up much better than traditional   methods. This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects. GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
% \bi
% \item
% This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
% GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).

% \item 
%  Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
%  is inherently more scalable.
%  \ei
% \begin{figure}[!t]
%     \centering
%     \includegraphics[width=\linewidth]{figs/cost.pdf}
%     \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
%     \label{fig:cost}
% \end{figure} 
Using GENERAL, we can  explore these research questions:
            \respto{1-6}

@@

            \begin{RQ}{
               Conventional bellwether method as proposed by krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects. In this experiment the conventional bellwether method is very expensive to find the ``bellwether''.}
            \end{RQ}

            \textbf{RQ2}:  How fast is new bellwether method aka GENERAL?

>>>>

\begin{document}
\title{   Finding GENERAL    Defect Prediction Models   
Within Hundreds  of   Software Projects}

@@

\IEEEtitleabstractindextext{%
\begin{abstract}
% \respto{2-22}{\color{blue}Given a group of software projects,
% there often exists  one   exemplar project
% that offers the best prediction for all others.
% Such ``bellwether projects''
% can be used to make quality predictions that are general
% to that group.}
% Existing  methods  for  finding bellwether  are  very slow.  When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers
% Hence,we  propose a faster way to find bellwethers. 
% GENERAL applies hierarchical clustering to groups of project data. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. This hierarchical method is a scalable approach to learning effective models from very
% large data sets. For  hundreds of projects, the defect prediction models generated from GENERAL's bellwether were just as good as those found via  standard methods.

\respto{2-22}{\color{blue}Given a group of software projects, there often exists  one   exemplar project that offers the best prediction for all others. Such ``bellwether projects'' can be used to make quality predictions that are general to that group.} Existing  methods  for  finding bellwether  are  very slow.  When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers. Also among a large group of software projects there may be subgroup of projects which are more similar to each other then other subgroups and can have a bellwether for each such subgroup of projects. Existing bellwether methods does not take this into consideration to find multiple bellwether. Hence, we  propose a faster and better  way to find bellwethers. GENERAL applies hierarchical clustering to groups of project data. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. This hierarchical method is a scalable approach to learning effective models from very large data sets. For  hundreds of projects, the defect prediction models generated from GENERAL's bellwether were just as good as those found via standard methods.

@@

\respto{1-2}\respto{1-3}{\color{blue} Researchers and industry practitioners makes use of data-driven decision making data mining algorithms build software quality models from project data.For example, many research and industrial groups generate defect predictors from software metrics~\cite{ghotra2015revisiting, zimm09 ,okutan2014software, he13, Zhang16aa, nam2017heterogeneous, Me13, Tantithamthavorn18, me09b, me10a, peters2015lace2, nam2018heterogeneous, menzies2011local, zimmermann09}. These metrics can take  forms including process metrics (that describe how and who updates the code) and product metrics (such as number of methods per class, lines of codes, etc). One advantage of this approach is that the collection of these metrics is very fast.
Also,  the subsequent data mining (to generate the quality models) can be fully automated and can scale to a large number of projects. Hence, data-driven decision making  is widely used in   SE research and   industrial practice.~\cite{tosun2010ai,kim2015remi,wan2018perceptions} }

\begin{table*}
\begin{center}
\includegraphics[width=14cm]{figs/istable.png}
\end{center}
\caption{Contradictory conclusions from OO-metrics studies for defect prediction. From~\cite{menzies2012local}, Studies report significant (``+'') or irrelevant (``-'') metrics verified by univariate prediction models. Blank entries indicate that the corresponding metric is not evaluated in that particular study.   CBO = coupling between objects; RFC = response for class (number of methods executed by arriving messages); LCOM = lack of cohesion (pairs of methods referencing one instance variable, different definitions of LCOM are aggregated); NOC = number of children (immediate subclasses); WMC = number os methods per class. For more details on these examples, and references to the papers containing these studies, see~\cite{menzies2012local}.}
\label{unstable}
\end{table*}

{\color{blue} But what is the external validity of the conclusions reached  via
the these data mining methods? Prior to this paper, the usual result is that such conclusions are not general to multiple projects. For example, Table~\ref{unstable} summarizes the results of dozens of studies. In that table we observe that, from project to project, very different attributes are most associated with defect prediction. This is troubling since,   as
Sawyer et al. argue,   project-general
insights are the key driver for businesses to invest in data analytics.
If  new models keep being generated whenever we switch to  new projects, then that exhausts the ability of  users to draw insight from  new data.
Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold. 
 Further,
if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
Lastly,
consider the task of training a   novice software engineers or newcomers to a project. If our models are not stable, then it hard to teach what factors  most influence software quality.}

@@

%{\color{blue} Finding general defect predictors  across many projects is a complex task.  
 %For a long list of   conclusions that were found to be  unstable across multiple projects, see~\cite{Me13}. This problem is so endemic in software engineering that other journals have devoted entire special issues to the topic~\cite{Menzies2012}.}

A new approach for transferring conclusions
across multiple projects
is     the ``bellwether'' method~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}.\respto{1-1a}\respto{2-2}{\color{blue} Given a community of projects developed by the same organization,
a ``bellwether'' is the   whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others} (and we call that the ``bellwether'' since that is the
name of the  leading sheep of a flock, with a bell on its neck).  This method:
\bi
\item Finds a  ``bellwether'' project that is exemplar for the rest;
\item Draw conclusions from  that project.
\ei
{\color{blue} \respto{1-1a}\respto{3-5}This approach is useful since bellwethers can generate
models that hold across multiple data sets.
Also,   bellwether are a better
way to transfer lessons between software projects~\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}  than many other methods including
the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.'s  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.}

% When new projects arrive, then even before there is much experience with those new projects,  models learned from other projects can be applied to the new project (just by studying the bellwether),
%  Further, \respto{2-2}{\color{blue} since the bellwether is an exemplar projects for the community of N projects seen so far},
%  %since the bellwether is similar to the other models
%  then when new projects appear, \respto{2-3}{\color{blue} bugs can be localized for that project} even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
 %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
 %or (b)~best practices to avoid quality problems;
 %or (c)~cost-benefit justifications for buying or building tools can be made stable across a large number 
 %of projects.

But existing  methods for bellwether transfer are very slow. When applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwethers.
%There are many reasons for that including how the models were certified (20 repeats  with different train/test sets)
%and the complexity of the analysis procedure (which includes fixing class imbalance and feature selection). But the major cause of this slow down was that those   methods  required an $O(N^2)$ comparison between   $N=697$ projects.

Accordingly, this paper explores a novel approach that can find  bellwethers much faster than standard methods.    
%dramatically improves on existing bellwether methods.
 {\color{blue}\respto{1-3a} Our GENERAL    algorithm uses hierarchical clustering  to recursively divide a large number of projects into smaller clusters. 
 Starting at the leaves of that tree of clusters, GENERAL finds the    bellwethers within sibling projects. That bellwether is then promoted up the tree. The output of GENERAL is the project promoted to the top of the tree of clusters. }
%Note that  GENERAL only needs
%to compare $O(m*(N/m)^2)$  projects to find the bellwether.

  GENERAL has two advantages over standard bellwether methods.
Firstly, 
according to several of the criteria studied here, GENERAL
can produce better predictors for software quality.  Secondly, it is much  
faster than standard bellwethers
(and scales to larger sets of data).

% \bi
% \item
% This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
% GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
% \item 
%  Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
%  is inherently more scalable.
%  \ei
% \begin{figure}[!t]
%     \centering
%     \includegraphics[width=\linewidth]{figs/cost.pdf}
%     \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
%     \label{fig:cost}
% \end{figure} 
To present GENERAL and to assess its value, this
paper asks and answers the following questions:
            \respto{1-6}

@@

            As a starting point for this research,  we need to document the problems associated with existing bellwether methods. RQ1 offers the following theoretical result:
            \begin{RQ}{
               Conventional bellwether method as proposed by Krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects.}
            \end{RQ}

            \textbf{RQ2}:  How fast is GENERAL bellwether?

            RQ2 explains the RQ1 result:
